Discrete Quantum Theories and Computing

### 2019-02-16 dissertation.tex
dissertation.lyx Acknowledgments Reviewed...

 &  & Supervisor &  &  &  &  & The application for ``Rethinking Foundations of Physics'' 2017 workshop
inspires Chapter~\ref{chap:Introduction}.\tabularnewline

@@

in the Tier 3 exam~\cite{Mathematics2018} are cited in Sec.~\ref{modalquantum}.\tabularnewline

@@

conjecture on Grassmannians studied with Prof.\ Dylan Paul Thurston
and the quantum interpretation discussed with Prof.\ Shouhong Wang
(汪守宏) also broadened my understanding on discrete and conventional
quantum theories. I would like to express my appreciation to all of
these.

To have the current content of the dissertation, I would also like
to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
I learned from the teachers in other courses also helped me consolidate
this dissertation as listed in Table~\ref{tab:teacher}. Even if
what taught by my other teachers are not directly related to this
dissertation, I must thank for your teaching to make me more mature
and easier to communicate with others, especially my English teachers,
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心).
\begin{table}[t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
dissertation, where IUB stands for Indiana University Bloomington
and NTU stands for National Taiwan University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Jin-Tzu~Chen}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Secs.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Secs.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}

Many people have done everything to make my double-major smooth. Moreover,

and to financially or specially support me during my \PhD study.
A comprehensive list is in my Curriculum Vitae at the end of the dissertation.
I need to thank all of them. Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the graduate
services assistant, Kate Forrest, and the directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
Science, I want to thank the graduate student office; the director
of AI/UI assignments, Charles Pope; the directors of \PhD study in
Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; and the infrastructure and technology group (ITG). Particularly,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. This computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by University Information
Technology Services (UITS). Indiana University Libraries was also
extremely helpful during my dissertation research. Except for a stack
of books I checked out directly, while the books are not in their
collection, I occasionally requested them via the Interlibrary Loan
service, recommended IU libraries to purchase them.

Except for the financial support via employment and award, I have
also supported by my family, especially my father Cheng-Tien Tai (戴振沺).
He always thinks one-step ahead and cares about my future more than
I do. Discussion with other family members and friends also helped
me to compose this dissertation or to do research in general, and
I want to thank following people which haven't been listed previously:\footnote{I only provide the Chinese name for some of them for three reasons.
First, I might only know their Chinese names. Second, there is no
unique way to translate a Chinese name to English, and I am not familiar
with any of them. Third, all these methods translate infinitely different
Chinese names to the same English name, so we lose some precision
or information if we only record their English name.}

@@

\item My other friends have office in Lindley or \textportuges{Luddy}
Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-Chieh
Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
Chandio}, Yuxiang Jiang (蒋宇翔), Pei-Ying Chen (陳珮瑩), Prof.~Qin Zhang
(张勤), Kaitlyn Owens, Praveen Narayanan, Liang Chen (陈亮), \textfrench{Ambrose
Bonnaire-Sergeant}, Ali Varamesh, Larry ``LP'' \textfrench{Ailes},
and Min-Chin Lin (林旻瑾), \ldots , etc.

\item My other family members, including, my mother Feng-Ming Chang
(張鳳鳴), my grandmother 戴許玉婷, my sister Sih-Sian Tai (戴司嫻), my cousins
Caren Liu (劉鈺平), and Kiwi Liu (劉子綺), \ldots , etc.

\item My official and nonofficial roommates, including Meng-Wei Chen
(陳孟瑋), Yu ``Larry'' Chen (陈煜), Kenshin Reita (禮田謙信), Jing-Han Liou
(劉經翰), Shu-Ling Wang (王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).

@@

\item My friends lived in the Tulip Tree Apartments, including Chao-Hong
Chen (陳昭宏), Tsaiyi Wu (吳采奕), Cheng ``Freddie'' Shi (史程), Ossama
Abdel~Gawwad, and Cathryn ``Cathy'' Creger-Chambers, \textbahasai{Sary
Silvhiany}, Shaozhuan Li (李绍颛), and Chenwei Zhang (张晨薇), Shu-Nan ``Nancy''
Chang (張舒涵), and Ching-Chi ``Victoria'' Chang (張靖琪), \ldots , etc.

@@

\item Other friends, including Yu-Jung Lin (林宇容), Winnie Lou (何慧芳),
Yi-Rong Yang (楊宜蓉), Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
Gong (龔治齊), and 江靜宜, \ldots , etc.

@@

Finally, I want to thank Blue Coat system for providing K9 Web Protection
to block distractive websites to keep me focus, and Jin-Ru Yang (楊謹如)
for keeping the password and helping me control myself in general.\end{acknowledgments*}

@@

\subsection{Cyclic Properties of Finite Fields}

@@

\subsection{Finite-Precision Extension of Gleason's Theorem}

>>>>

 &  & Supervisor &  &  &  &  & The application for \emph{Rethinking Foundations of Physics} 2017
workshop inspires Chapter~\ref{chap:Introduction}.\tabularnewline

@@

in the Tier 3 exam~\cite{Mathematics2018} are cited in Chapters~\ref{chap:Introduction}
and~\ref{chap:Unrestricted-Finite-Fields}.\tabularnewline

@@

conjecture~\cite{hartshorne1977algebraic} on Grassmannians studied
with Prof.\ Dylan Paul Thurston and the quantum interpretation discussed
with Prof.\ Shouhong Wang (汪守宏) also broadened my understanding on
discrete and conventional quantum theories. I would like to express
my appreciation to all of these.

To have the current content of dissertation, I would also like to
thank John Gardiner for some inspiring discussion about quantum probability
measures over finite fields~\cite{Gardiner2014}. His research supervised
by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
I learned from the teachers in other courses also helped me consolidate
this dissertation as listed in Table~\ref{tab:teacher}. Learning
other materials also made me more mature and easier to communicate
with others. I need to thank those who taught me, especially my English
teachers, Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心).

\begin{table}[!t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
dissertation, where IUB stands for Indiana University Bloomington
and NTU stands for National Taiwan University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Chou~(周謀鴻)}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Secs.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{discretequantumtheoryIIb}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Secs.~\ref{subsec:Two-dimensional-Hilbert-Space}, \ref{subsec:Cyclic-Properties-of},
\ref{subsec:Complexified-Finite-Fields}, and~\ref{discretequantumtheoryIIb}.\tabularnewline
\midrule 
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\midrule
Mo-Hong\linebreak[3] Chou (周謀鴻) & NTU & 221~U4290 & The textbook~\cite{GolubVanLoan1996} of \emph{Introduction to Computational Linear Algebra}
is cited in Sec.~\ref{subsec:Finite-Precision-Extension-of}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}
Many people have done everything to make my double-major smooth. I
need to thank all of their supports, financially or providing some
experience, as listed in my Curriculum Vitae at the end of the dissertation.
Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the graduate
services assistant, Kate Forrest, and the directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
Science, I want to thank the graduate student office; the director
of AI/UI assignments, Charles Pope; the directors of \PhD study in
Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; and the infrastructure and technology group (ITG). Particularly,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. This computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by University Information
Technology Services (UITS). Indiana University Libraries was also
extremely helpful during my dissertation research. Except for a stack
of books I checked out directly, while the books are not in their
collection, I occasionally requested them via the Interlibrary Loan
service or recommended IU libraries to purchase them.

Except for the financial support via employment and award, I have
also supported by my family, especially my father Cheng-Tien Tai (戴振沺).
He always thinks one-step ahead and cares about my future more than
I do. Discussion with other family members and friends also helped
me to compose this dissertation, to do research, or to live better
in general, and I want to thank the following people which haven't
been listed previously:\footnote{For some of them, I only provide their Chinese names for two reason.
First, I might only know their Chinese names. Second, there are many
ways to translate a name to English, but I don't know which one they
choose.}

@@

\item My other friends having an office in Lindley or \textportuges{Luddy}
Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-Chieh
Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
Chandio}, Yuxiang Jiang (蒋宇翔), Lei Wang (王磊), Diyue Bu (卜廸悦), Pei-Ying
Chen (陳珮瑩), Prof.~Qin Zhang (张勤), Kaitlyn Owens, Praveen Narayanan,
Liang Chen (陈亮), \textfrench{Ambrose Bonnaire-Sergeant}, Ali Varamesh,
Larry ``LP'' \textfrench{Ailes}, and Min-Chin Lin (林旻瑾), \ldots ,
etc.

\item My other family members, including my mother Feng-Ming Chang
(張鳳鳴), my grandmothers 戴許玉婷 and 張林枝, my sister Sih-Sian Tai (戴司嫻),
my cousins especially Caren Liu (劉鈺平) and Kiwi Liu (劉子綺), and my
aunts and uncles, \ldots , etc.

\item My roommates, including Meng-Wei Chen (陳孟瑋), Yu ``Larry''
Chen (陈煜), Kenshin Reita (禮田謙信), and Jing-Han Liou (劉經翰).

@@

\item My friends living in the Tulip Tree Apartments, including Chao-Hong
Chen (陳昭宏), Tsaiyi Wu (吳采奕), Cheng ``Freddie'' Shi (史程), Ossama
Abdel~Gawwad, and Cathryn ``Cathy'' Creger-Chambers, \textbahasai{Sary
Silvhiany}, Shaozhuan Li (李绍颛), Chenwei Zhang (张晨薇), Shu-Nan ``Nancy''
Chang (張舒涵), and Ching-Chi ``Victoria'' Chang (張靖琪), \ldots , etc.

@@

\item Other friends, including Shu-Ling Wang (王舒齡), Wan-Ling ``Wynnie''
Chang (張婉鈴), Yu-Jung Lin (林宇容), Winnie Lou (何慧芳), Yi-Rong Yang (楊宜蓉),
Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
Gong (龔治齊), and 江靜宜, \ldots , etc.

@@

Finally, I want to thank K9 Web Protection for blocking distractive
websites to keep me focus, and Jin-Ru Yang (楊謹如) for keeping the password
and helping me control myself in general.\end{acknowledgments*}

@@

\subsection{Cyclic Properties of Finite Fields\label{subsec:Cyclic-Properties-of}}

@@

\subsection{Finite-Precision Extension of Gleason's Theorem\label{subsec:Finite-Precision-Extension-of}}
